---
title: "Ruggeri et al 2022 Author diversity calculation"
author: "Sakshi"
date: "2023-02-15"
output: html_document
---

In this script, we compute author diversity by using author's institution affiliation as a proxy. We first coded all 171 author names and their  institution affiliation using the Global North-South classification. To measure this, we followed the United Nations' Finance Center for South-South Cooperation (http://www.fc-ssc.org/en/partnership_program/south_south_countries), which is considered as a reliable source including a list of 78 countries (including Korea and Singapore which are highly developed country and part of the Four Asian Tigers). We also corroborated this list by following the Human Development Index (HDI) and ITU’s Telecommunication Development Bureau region classifications (https://www.itu.int/en/ITU-D/Statistics/Pages/definitions/regions.aspx) which suggests that the Global South broadly comprise Africa, Latin America and the Caribbean, and Asia (without Israel, Japan, Singapore, and the Republic of Korea).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#####################
## Load Libraries ##
#####################

```{r}
if (!require("pacman")) install.packages("pacman")             # install the package manager pacman

# load packages with "p_load"
pacman::p_load("tidyverse", "readxl", "plyr", "ggplot2", "gtsummary", "knitr", "maps", "mapproj", "ggpubr")

knitr::opts_chunk$set(echo = TRUE)

```

#####################
## Import the data ##
#####################

```{r}

# first remove existing variables from the working space
rm(list=ls())

# load data 
# setwd()
df <- read_excel('Ruggeri et al 2022_author diversity.xlsx') %>%
  dplyr::rename(Region_affiliation = "Region",
                Area_affiliation = "Area")


```
#####################
## Author Country Diversity ##
#####################

We calculate the number of studies based on global area, author affiliation 
```{r}
#Region-wise distribution 
prop.table(table(df$"Region_affiliation")) 

#Display the number of studies for each global area (Global North vs Global South)
table(df$'Author Country Affiliation')
prop.table(table(df$Area_affiliation))

#Create a table 
region <- select(df, c("Region_affiliation", "Area_affiliation", "Author Country Affiliation"))
region

#Save a descriptive table of author diversity by country
region_table <- region |> tbl_summary(
    by = Area_affiliation,
    missing = "no",
  ) %>%
  add_overall() %>% # add column with total number of non-missing observations
  modify_header(label = "**Global regions**") %>% # update the column header
  bold_labels() 
region_table 

#save the region-wise table
#region_table  %>% as_flex_table() %>% 
  #flextable::save_as_docx(path = "//author.docx")

``` 

#####################
## Author Country visualisations ##
#####################

First, we plot only Global South countries
```{r}
#Load World map data 
WorldData <- map_data('world') %>% filter(region != "Antarctica") %>% fortify

#Select Global South author data 
df <- data.frame(region=c('Lebanon','Nepal','Brazil', "México", "Kazakhstan", "China", 
                          "Nigeria", "Egypt", "Indonesia", "Argentina", "Iran", "South Africa", "Paraguay"), 
                 value=c(1, 2, 2, 1, 2, 4, 2, 1, 2, 2, 1, 1, 1), 
                 stringsAsFactors=FALSE)


#Plot Global South author country data
plot1 <- ggplot() +
    geom_map(data = WorldData, map = WorldData,
                  aes(x = long, y = lat, group = group, map_id=region),
                  fill = "white", colour = "#C6DBEF", size=0.5) + 
    geom_map(data = df, map=WorldData,
                  aes(fill=value, map_id=region),
                  colour="#C6DBEF", size=0.5) +
    coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) + 
    colorspace::scale_fill_continuous_sequential(palette = "Blues", 
                                               begin = .18, end = .99) +
    scale_y_continuous(breaks=c()) +
    scale_x_continuous(breaks=c()) +
    labs(fill="legend", title="Global South Affiliation", x="", y="") +
  theme_classic() +
theme(legend.position = "bottom", 
        legend.key.size = unit(0.7, 'cm'),
        strip.background = element_blank(), panel.spacing = unit(4, "mm"), panel.background = element_blank())
   
plot1 

# save the plot 
# ggsave("fig2.pdf", plot1, device = "pdf", width=18, height = 15)
``` 


*All author country affiliation plot*
#Authors were affiliated to the following countries based in the Global South - 
#The following countries were represented: 'Lebanon','Nepal','Brazil', "México", "Kazakhstan", "China", "Nigeria", "Egypt", "Indonesia", "Argentina", "Iran", "South Africa", "Paraguay"
#11 were not represented: "Jordon", "India", "Turkey", "Pakistan", "Panama", "Vietnam", "Malaysia", "Kenya", "Ghana", "Ethiopia", Uruguay
```{r}

#Select all author country data 
df3 <- data.frame(region=c('Lebanon','Nepal','Brazil', "México", "Kazakhstan", "China", "Taiwan","Singapore", "Nigeria", "Egypt", "Indonesia", "Argentina", "Iran", "South Africa", "Paraguay", "USA", "UK", "Australia", "Austria", "Belgium", "Bulgaria", "Canada", "Croatia", "Czech Republic", "Denmark", "Estonia", "France", "Georgia", "Germany", "Hungary", "Ireland", "Italy", "Israel", "Japan", "Netherlands", "North Macedonia", "Norway", "Poland", "Portugal", "Republic of Korea", "Serbia", "Romania", "Slovenia","Spain","Sweden", "Ukraine", "Switzerland", "Bosnia_and_Herzegovina", "Moldova", "Montenegro", "Slovakia", "Jordon", "India", "Turkey", "Pakistan", "Panama", "Vietnam", "Malaysia", "Kenya", "Uruguay", "Ghana", "Ethiopia"), 
                 value=c(1,2,2,1, 2, 4, 4,2, 2, 1, 2, 3, 1, 1, 1, 35, 27, 1, 3, 3, 3, 2, 3, 5, 3, 1, 1, 1, 9, 1, 1, 4, 1, 3, 10, 1, 5, 2, 2, 1, 8, 3, 2, 2, 1, 2, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
                 stringsAsFactors=FALSE)


#Plot all author country data
plot2 <- ggplot() +
    geom_map(data = WorldData, map = WorldData,
                  aes(x = long, y = lat, group = group, map_id=region),
                  fill = "white", colour = "#C6DBEF", size=0.5) + 
    geom_map(data = df3, map=WorldData,
                  aes(fill=value, map_id=region),
                  colour="#C6DBEF", size=0.5) +
    coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) + 
    colorspace::scale_fill_continuous_sequential(palette = "Blues", 
                                               begin = .18, end = .99) +
    scale_y_continuous(breaks=c()) +
    scale_x_continuous(breaks=c()) +
    labs(fill="legend", title="Author Institution Affiliation", x="", y="") +
  theme_classic() +
theme(legend.position = "bottom", 
        legend.key.size = unit(0.7, 'cm'),
        strip.background = element_blank(), panel.spacing = unit(4, "mm"), panel.background = element_blank())


plot2

ggsave("fig2.pdf", plot2, device = "pdf", width=18, height = 15)

``` 



