---
title: "Ruggeri et al 2022"
author: "Sakshi"
date: "2023-02-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#####################
## Load Libraries ##
#####################

```{r}
#download packages
packages <- c("tidyverse", "readxl", "plyr", "ggplot2")
invisible(lapply(packages, library, character.only = TRUE))
rm(packages)

```

#####################
## Import the data ##
#####################

```{r}

#first remove existing variables from the working space
rm(list=ls())

#load data 
#setwd()
df <- read_excel('/Users/sakshighai/Desktop/Ruggeri et al 2022_author diversity.xlsx')

```
#####################
## Author Country Diversity ##
#####################

We calculate the number of studies based on global area, author affiliation 
```{r}

#PBS Courses 
prop.table(table(df$"Region")) 

#Display the number of studies for each global area (Global North vs Global South)
prop.table(table(df$Area))

#Display the number of studies for each global area (Global North vs Global South)
prop.table(table(df$`Underepresented Countries`))

```
#####################
## Visualizing author diversity  ##
#####################

Out of 25 Global South countries sampled, 14 countries represented: Lebanon, Nepal, Brazil, México, Kazakhstan, China, Singapore, Nigeria, Egypt, Indonesia, Argentina, Iran, South Africa, Paraguay. 11 Countries that were not represented Ethiopia, Ghana, India, Jordan, Kenya, Malaysia, Pakistan, Turkey, Vietnam, Panama, Turkey

```{r}

#Load World map data 
WorldData <- map_data('world') %>% filter(region != "Antarctica") %>% fortify

#Select Global South author data 
df <- data.frame(region=c('Lebanon','Nepal','Brazil', "México", "Nepal", "Brazil", "Kazakhstan", "China", "Singapore", "Nigeria", "Egypt", "Indonesia", "Argentina", "Iran", "South Africa", "Paraguay"), 
                 value=c(1,2,2,1,1, 2, 2, 4, 2, 2, 1, 2, 3, 1, 1, 1), 
                 stringsAsFactors=FALSE)


#Plot Global South author country data
plot1 <- ggplot() +
    geom_map(data = WorldData, map = WorldData,
                  aes(x = long, y = lat, group = group, map_id=region),
                  fill = "white", colour = "#7f7f7f", size=0.5) + 
    geom_map(data = df, map=WorldData,
                  aes(fill=value, map_id=region),
                  colour="#7f7f7f", size=0.5) +
    coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) + 
    colorspace::scale_fill_continuous_sequential(palette = "Blues", 
                                               begin = .07, end = .79) +
    scale_y_continuous(breaks=c()) +
    scale_x_continuous(breaks=c()) +
    labs(fill="legend", title="Global South Author Affilation", x="", y="") +
    theme_bw()
plot1 


library(ggpubr)


#Select all author country data 
df3 <- data.frame(region=c('Lebanon','Nepal','Brazil', "México", "Kazakhstan", "China", "Singapore", "Nigeria", "Egypt", "Indonesia", "Argentina", "Iran", "South Africa", "Paraguay", "USA", "UK", "Australia", "Austria", "Belgium", "Bulgaria", "Canada", "Croatia", "Czech Republic", "Denmark", "Estonia", "France", "Georgia", "Germany", "Hungary", "Ireland", "Italy", "Israel", "Japan", "Netherlands", "North Macedonia", "Norway", "Poland", "Portugal", "Republic of Korea", "Serbia", "Romania", "Slovenia","Spain","Sweden", "Ukraine", "Switzerland", "Bosnia_and_Herzegovina", "Moldova", "Montenegro", "Slovakia", "Jordon", "India", "Turkey", "Pakistan", "Panama", "Vietnam", "Malaysia", "Kenya", "Jordon", "Ghana", "Ethipia"), 
                 value=c(1,2,2,1, 2, 4, 2, 2, 1, 2, 3, 1, 1, 1, 35, 27, 1, 3, 3, 3, 2, 3, 5, 3, 1, 1, 1, 9, 1, 1, 4, 1, 3, 10, 1, 5, 2, 2, 1, 8, 3, 2, 2, 1, 2, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), 
                 stringsAsFactors=FALSE)

#Plot all author country data
plot2 <- ggplot() +
    geom_map(data = WorldData, map = WorldData,
                  aes(x = long, y = lat, group = group, map_id=region),
                  fill = "white", colour = "#C6DBEF", size=0.5) + 
    geom_map(data = df3, map=WorldData,
                  aes(fill=value, map_id=region),
                  colour="#C6DBEF", size=0.5) +
    coord_map("rectangular", lat0=0, xlim=c(-180,180), ylim=c(-60, 90)) + 
    colorspace::scale_fill_continuous_sequential(palette = "Blues", 
                                               begin = .18, end = .99) +
    scale_y_continuous(breaks=c()) +
    scale_x_continuous(breaks=c()) +
    labs(fill="legend", title="Author Country Affiliation", x="", y="") +
    theme_bw()


plot2

  

```